---
title: "HW6"
author: "Nick Grieco"
editor: visual
format:
  pdf:
    embed-resources: true
execute:
  echo: true
  message: false
  warning: false
---

```{r setup}
library(tidyverse)
library(tidytext)
library(schrute)
library(ggplot2)
```

# The Office

Let's continue to work with *The Office* text from the [schrute](https://cran.r-project.org/web/packages/schrute/index.html) package.

# Sentiment Analysis

### Over Time

Calculate the sentiment score (positive - negative) for each episode, and plot this variable over time.

```{r}
sentiments <- tidytext::sentiments

sent <- theoffice %>%
    unnest_tokens(word, text) %>%
    inner_join(sentiments, by = "word") %>%
    group_by(season,episode) %>%
    summarize(pos_score = sum(sentiment == "positive"),
            neg_score = sum(sentiment == "negative"),
            sent_score = pos_score - neg_score,
            .groups = "drop") %>%
    arrange(season, episode) %>%
    mutate(episode = row_number()) %>%
    select(episode,sent_score)

ggplot(sent, aes(x = episode, y = sent_score)) +
  geom_line() +
  labs(
    title = "Sentiment Score Over Time in The Office",
    x = "Episode Number Overall",
    y = "Sentiment Score"
  ) +
  theme_minimal()
```

### By Rating

Create a scatterplot of the `imdb_rating` versus the sentiment score (positive - negative), where the case is again an episode. Decide whether a linear model is a good fit to this relationship (optional, if you have had modeling classes, what model looks best?). Comment on what you find.

```{r}
sent2 <- theoffice %>%
    unnest_tokens(word, text) %>%
    inner_join(sentiments, by = "word") %>%
    group_by(season,episode) %>%
    summarize(pos_score = sum(sentiment == "positive"),
            neg_score = sum(sentiment == "negative"),
            sent_score = pos_score - neg_score,
            imdb_rating = mean(imdb_rating),
            .groups ="drop") %>%
    arrange(season, episode) %>%
    mutate(episode = row_number()) %>%
    select(episode,sent_score,imdb_rating)

ggplot(sent2, aes(x = sent_score, y = imdb_rating)) +
  geom_point() +  
  geom_smooth(method = "lm") + 
  labs(
    title = "IMDb Rating vs Sentiment Score per Episode of The Office",
    x = "Sentiment Score",
    y = "IMDb Rating"
  ) +
  theme_minimal()
```

I would say a linear model is not a great fit to this relationship. It feels pretty random overall.

### Sentiment Negation

Identify at least a few negations that change the sentiment values based on the text. Use this to recreate the graphs above (or do this first, then create the graphs).

```{r}
bigrams <- theoffice %>% 
    unnest_tokens(bigram,text,"ngrams", n=2) %>%
    drop_na(bigram) %>%
    separate(bigram,
             into=c("word1","word2"),
             sep=" ",
             remove=F) %>%
    inner_join(sentiments,
               by=c("word2"="word")) %>%
    mutate(sentiment = ifelse(word1 == "no" | word1 == "not",
                ifelse(sentiment == "positive", "negative", "positive"),
                sentiment)) 

sent3 <- bigrams %>%
    group_by(season, episode) %>%  
    summarize(pos_score = sum(sentiment == "positive"),
            neg_score = sum(sentiment == "negative"),
            sent_score = pos_score - neg_score,
            imdb_rating = mean(imdb_rating),
            .groups ="drop") %>%
    arrange(season, episode) %>%
    mutate(episode = row_number()) %>%
    select(episode,sent_score,imdb_rating)
```

```{r}
ggplot(sent3, aes(x = episode, y = sent_score)) +
  geom_line() +
  labs(
    title = "Sentiment Score Over Time in The Office",
    subtitle = "With Sentiment Negation Included (no, not)",
    x = "Episode Number Overall",
    y = "Sentiment Score"
  ) +
  theme_minimal()
```

```{r}
ggplot(sent3, aes(x = sent_score, y = imdb_rating)) +
  geom_point() +  
  geom_smooth(method = "lm") + 
  labs(
    title = "IMDb Rating vs Sentiment Score per Episode of The Office",
    subtitle = "With Sentiment Negation Included (no, not)",
    x = "Sentiment Score",
    y = "IMDb Rating"
  ) +
  theme_minimal()
```
